---
title: "Starting with tuicalendr"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{starting-with-tuicalendr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(tuicalendr)
```


## Create a calendar

Create a new calendar with function `calendar`:

```{r}
calendar()
```

Default view is "week", you can also choose "day" or "month":

```{r}
calendar(defaultView = "month")
```

You can use some options to customize the calendar:

```{r}
calendar(defaultView = "month") %>% 
  set_month_options(
    startDayOfWeek = 1,
    daynames = c("Dim", "Lun", "Mar", "Mer", "Jeu", "Ven", "Sam"),
    narrowWeekend = TRUE
  )
```


## Add schedules

Add task and planning with `add_schedule`:

```{r}
calendar(defaultView = "day") %>% 
  add_schedule(
    title = "R - introduction", 
    body = "What is R?",
    start = sprintf("%s 08:00:00", Sys.Date()),
    end = sprintf("%s 12:30:00", Sys.Date()),
    category = "time"
  ) %>% 
  add_schedule(
    title = "R - visualisation", 
    body = "With ggplot2",
    start = sprintf("%s 13:30:00", Sys.Date()),
    end = sprintf("%s 18:00:00", Sys.Date()),
    category = "time"
  ) %>% 
  add_schedule(
    title = "Basile birthday", 
    body = "Don't forget!",
    start = Sys.Date(),
    end = Sys.Date(),
    category = "allday"
  ) %>% 
  add_schedule(
    title = "Lunch", 
    body = "With Fanny",
    start = sprintf("%s 12:00:00", Sys.Date()),
    end = sprintf("%s 14:00:00", Sys.Date()),
    category = "time"
  )
```


You can also use a `data.frame` containing schedules:

```{r}
my_schedules <- data.frame(
  title = c("R - introduction", "R - visualisation",
            "Basile birthday", "Lunch"), 
  body = c("What is R?", "With ggplot2", "Don't forget!", "With Fanny"),
  start = c(sprintf("%s 08:00:00", Sys.Date()), sprintf("%s 13:30:00", Sys.Date()),
            format(Sys.Date()), sprintf("%s 12:00:00", Sys.Date())),
  end = c(sprintf("%s 12:30:00", Sys.Date()), sprintf("%s 18:00:00", Sys.Date()), 
          format(Sys.Date()), sprintf("%s 14:00:00", Sys.Date())),
  category = c("time", "time", "allday", "time")
)

calendar(defaultView = "day") %>% 
  add_schedule_df(my_schedules)
```


Define calendars properties to add color and group schedules into groups (you'll need to use a `calendarId` into your shedules):

```{r}
my_schedules$calendarId <- c("courses", "courses", "birthdays", "social")

calendar(defaultView = "day") %>% 
  set_calendars_props(id = "courses", name = "Courses", color = "#FFF", bgColor = "#E41A1C") %>%
  set_calendars_props(id = "birthdays", name = "Birthdays", color = "#FFF", bgColor = "#377EB8") %>%
  set_calendars_props(id = "social", name = "Social", color = "#FFF", bgColor = "#4DAF4A") %>%
  add_schedule_df(my_schedules)
```



A monthly calendar (with navigation buttons) : 

```{r}
my_schedules <- data.frame(
  calendarId = c("courses", "courses", "birthdays", "social"),
  title = c("R - introduction", "R - visualisation",
            "Basile birthday", "Lunch"), 
  body = c("What is R?", "With ggplot2", "Don't forget!", "With Fanny"),
  start = c(sprintf("%s 08:00:00", Sys.Date() - 3), sprintf("%s 13:30:00", Sys.Date() + 1),
            format(Sys.Date() - 7), sprintf("%s 12:00:00", Sys.Date() + 7)),
  end = c(sprintf("%s 12:30:00", Sys.Date()), sprintf("%s 18:00:00", Sys.Date() + 6), 
          format(Sys.Date() - 7), sprintf("%s 14:00:00", Sys.Date() + 7)),
  category = c("allday", "allday", "allday", "time")
)

calendar(defaultView = "month", useNav = TRUE) %>% 
  set_calendars_props(id = "courses", name = "Courses", color = "#FFF", bgColor = "#E41A1C") %>%
  set_calendars_props(id = "birthdays", name = "Birthdays", color = "#FFF", bgColor = "#377EB8") %>%
  set_calendars_props(id = "social", name = "Social", color = "#FFF", bgColor = "#4DAF4A") %>%
  add_schedule_df(my_schedules)
```


<br>
<br>
<br>
